---
title: "German & Polish analysis"
author: "Bodo Winter"
date: "9/3/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Preprocessing

Load libraries:

```{r libs, message = FALSE}
library(tidyverse)
library(stringr)
```

Let's load in the data files:

```{r load_files, message = FALSE}
pol <- read_delim('../data/2018-08-21-polish.txt', delim = '\t')
ger <- read_delim('../data/2018-08-21-german.txt', delim = '\t')

# Check:

ger %>% print(width = Inf, n = 2)
```

Selected only those columns needed (for now):

```{r rid_cols}
ger <- select(ger,
              sessionid,
              inputvalue, options,
              repetitions)
pol <- select(pol,
              sessionid,
              inputvalue, options,
              repetitions)
```

(We are going to ignore "foreignlanguages" for now.)

So, Ola/Suse: I presume sessionid can be used to identify participants? In that case, let's rename this to subject:

```{r renaming}
ger <- rename(ger,
              sub = sessionid,
              input = inputvalue)
pol <- rename(pol,
              sub = sessionid,
              input = inputvalue)
```

Get rid of those that didn't complete the full experiment:

```{r incompletes}
# Table with how many data points there are per subject:

ger_subs <- table(ger$sub)
pol_subs <- table(pol$sub)

# Get those that do not have 104 data points:

bad_germans <- names(ger_subs)[which(ger_subs != 104)]
bad_poles <- names(pol_subs)[which(pol_subs != 104)]

## How many are there that need to be excluded?

length(bad_germans)
length(bad_poles)

## Out of how many in total?

length(ger_subs)
length(pol_subs)

## So that's how much exclusion?

round(length(bad_germans) / length(ger_subs), 2)
round(length(bad_poles) / length(pol_subs), 2)

# Extract them:

ger <- filter(ger, !(sub %in% bad_germans))
pol <- filter(pol, !(sub %in% bad_poles))
```

Is this right that 41% of all Polish participants didn't complete the experiment? For Germans it's 27%.

Next, I want to extract the relevant options bit. This is really ugly for now (will think of a more elegant regex one-liner soon):

```{r extract_options}
# Extract response string by splitting at the bracket:

ger_resp <- str_split(ger$options, '\\[', simplify = TRUE)[, 2]
pol_resp <- str_split(pol$options, '\\[', simplify = TRUE)[, 2]

# Get rid of first two special characters:

ger_resp <- str_sub(ger_resp, 2, str_length(ger_resp))
pol_resp <- str_sub(pol_resp, 2, str_length(pol_resp))

# Take the word out:

suppressWarnings(ger$choice <- separate(tibble(ger_resp),
                                        ger_resp, into = LETTERS)[, 1]$A)
suppressWarnings(pol$choice <- separate(tibble(pol_resp),
                                        pol_resp, into = LETTERS)[, 1]$A)

## Let's get rid of the options column:

ger <- select(ger, -options)
pol <- select(pol, -options)

# Sanity-check: How does inputvalue versus choice look like?

select(ger, input, choice)
select(pol, input, choice)
```

Let's get rid of any subject that has gotten the clapping wrong at least once:

```{r clap_exclude}
# Subset of clapping items:

ger_claps <- filter(ger, input == 'Klatschen')
pol_claps <- filter(pol, input == 'klaskanie')

# Get all the wrong claps:

bad_germans <- ger_claps$input != ger_claps$choice
bad_poles <- pol_claps$input != pol_claps$choice

# Get the subjects for which the claps were wrong:

bad_germans <- unique(ger_claps$sub[bad_germans])
bad_poles <- unique(pol_claps$sub[bad_poles])

# How many subjects do we have right now?

length(unique(ger$sub))
length(unique(pol$sub))

# Extract the wrong-clappers:

ger <- filter(ger,
              !(sub %in% bad_germans))
pol <- filter(pol,
              !(sub %in% bad_poles))
```

Let's get rid of the kiki and bouba and r/l stims, as well as the clapping items:

```{r kiki_r_l_extract}
# Define vector of trials to extract:

bad_trials <- c('r', 'l', 'kiki', 'bouba', 'klaskanie', 'Klatschen')

# Get rid of those trials:

ger <- filter(ger,
              !(input %in% bad_trials))
pol <- filter(pol,
              !(input %in% bad_trials))
```

Let's check whether this work. Everybody should have 90 data points now (3 * 30).

```{r check}
table(ger$sub)
table(pol$sub)
```

Why are there still people with more than 90 data points?

Each item should occur in equal proportions:

```{r input_check}
table(ger$input)
table(pol$input)
```

This does not seem to be right: How come we have only two "zbierać", and shouldn't all be in equal proportions anyway?

## Check accuracy:

Let's create an accuracy measure, numerical with 0 = inaccurate and 1 = accurate.

```{r acc_create}
ger <- mutate(ger,
              ACC = ifelse(input == choice, 1, 0))
pol <- mutate(pol,
              ACC = ifelse(input == choice, 1, 0))
```

Let's check the average accuracy:

```{r avg_acc}
round(mean(ger$ACC), 2)
round(mean(pol$ACC), 2)
```

69% for the Germans and 60% for the Poles? That seems a bit high?

Let's check accuracy per concept:

```{r acc_per_concept}
ger %>% group_by(input) %>%
  summarize(ACC = mean(ACC)) %>%
  mutate(ACC = round(ACC, 2)) %>% 
  arrange(desc(ACC)) %>% 
  print(n = Inf)
pol %>% group_by(input) %>%
  summarize(ACC = mean(ACC)) %>%
  mutate(ACC = round(ACC, 2)) %>% 
  arrange(desc(ACC)) %>% 
  print(n = Inf)
```

Check average per subject:

```{r avg_per_sub}
ger %>% group_by(sub) %>%
  summarize(ACC = mean(ACC)) %>% 
  mutate(ACC = round(ACC, 2)) %>% 
  print(n = Inf)
pol %>% group_by(sub) %>%
  summarize(ACC = mean(ACC)) %>% 
  mutate(ACC = round(ACC, 2)) %>% 
  print(n = Inf)
```


